Tree size, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2019-09-18 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd

### Introduction
Forests globally play a critical role in climate regulation ([Bonan 2008](https://science.sciencemag.org/content/320/5882/1444)), yet there remains enormous uncertainty as to how the terrestrial carbon (C) sink, which is dominated by forests, will respond to climate change ([Friedlingstein et al. 2006](https://journals.ametsoc.org/doi/full/10.1175/JCLI3800.1)). An important aspect of this uncertainty lies in responses to drought (**REF**). In many forested regions around the world, the risk of severe drought is increasing ([Trenbert et al. 2014](https://www.nature.com/articles/nclimate2067)), even in conjunction with increasing precipitation ([IPCC 2014](https://www.cambridge.org/core/books/climate-change-2014-impacts-adaptation-and-vulnerability-part-b-regional-aspects/036A899BD52861D61B0D519C5F2B9334)). Global change-type drought has been affecting forests worldwide ([Allen et al. 2015](https://doi.org/10.1016/j.foreco.2009.09.001)), and it is expected that future climate change-driven droughts will severely impact forests around the world ([Allen et al. 2015](https://doi.org/10.1016/j.foreco.2009.09.001); **REFS**). Larger trees tend to suffer more (e.g., [@bennett_larger_2015]; Stovall et al. 2019), resulting in disproportionate impacts on forest C storage ([Meakem et al. 2018](https://nph.onlinelibrary.wiley.com/doi/10.1111/nph.14633)). As a result, forest drought responses stand to strongly impact forest feedbacks to climate change (**REFS**), yet accurate characterization of drought responses remains a modeling challenge (**REFS**)-- in part because some of the mechanisms underlying drought responses remain unclear. Understanding forest responses to drought requires increased functional understanding of how tree size, microhabitat, and species' traits jointly confer individual-level vulnerability or resistance, and whether their influence is consistent across droughts.

@@

**misc content to integrate**
From [@kannenberg_linking_2019], species with diffuse porous wood anatomy (*Liriodendron*) are more sensitive to drought, whereas ring-porous are not as affected because they more easily rebuild structures for hydraulic conductivity. This paper mentions it would be good to have this data with respect to latent affects from drought.
\newpage
### Acknowledgements
words

>>>>

### Introduction
Forests globally play a critical role in climate regulation ([Bonan 2008](https://science.sciencemag.org/content/320/5882/1444)), yet there remains enormous uncertainty as to how the terrestrial carbon (C) sink, which is dominated by forests, will respond to climate change ([Friedlingstein et al. 2006](https://journals.ametsoc.org/doi/full/10.1175/JCLI3800.1)). An important aspect of this uncertainty lies in responses to drought (**REF**). In many forested regions around the world, the risk of severe drought is increasing ([Trenbert et al. 2014](https://www.nature.com/articles/nclimate2067)), even in conjunction with increasing precipitation ([IPCC 2014](https://www.cambridge.org/core/books/climate-change-2014-impacts-adaptation-and-vulnerability-part-b-regional-aspects/036A899BD52861D61B0D519C5F2B9334)). Global change-type drought has been affecting forests worldwide ([Allen et al. 2015](https://doi.org/10.1016/j.foreco.2009.09.001)), and it is expected that future climate change-driven droughts will severely impact forests around the world ([Allen et al. 2015](https://doi.org/10.1016/j.foreco.2009.09.001); **REFS**). Larger trees tend to suffer more (e.g., [@bennett_larger_2015]; Stovall et al. 2019), resulting in disproportionate impacts on forest C storage ([Meakem et al. 2018](https://nph.onlinelibrary.wiley.com/doi/10.1111/nph.14633)). As a result, forest drought responses stand to strongly impact forest feedbacks to climate change (**REFS**), yet accurate characterization of drought responses remains a modeling challenge (**REFS**)-- in part because some of the mechanisms underlying drought responses remain unclear. Understanding forest responses to drought requires increased functional understanding of how tree size, microhabitat, and species' traits jointly confer individual-level vulnerability or resistance, and the extent to which their influence is consistent across droughts.

@@

**misc content to integrate**
From [@kannenberg_linking_2019], species with diffuse porous wood anatomy (*Liriodendron*) are more sensitive to drought, whereas ring-porous are not as affected because they more easily rebuild structures for hydraulic conductivity. This paper mentions it would be good to have this data with respect to latent affects from drought.
\newpage
### Acknowledgements
funding: ForestGEO,
